Nonparametric Goodness-of-Fit Tests for Discrete Null Distributions

### 2011-08-24 rjournal/AE.tex
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/ks-test@59 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

This paper presents a revision of R's
\code{ks.test()} function and a new \code{cvm.test()} function to
fill this void for researchers and practitioners in the R environment
\citep{R2010}. This
work was motivated by the need for such goodness-of-fit testing in a study
of Olympic figure skating scoring \citep{emersonarnold2010}.  
We first present overviews of the theory and general implementation of the
discrete Kolmogorov-Smirnov and Cram\'{e}r-von Mises tests.  We discuss
the particular implementation of the tests in R and provide examples.  We
conclude with a short discussion, including the state of existing continuous
and two-sample Cram\'{e}r-von Mises testing in R.

@@

Having obtained the test statistic, the $p$-value must then be calculated. 
For larger sample sizes, the null distribution can be approximated
with the null distribution from the classical Kolmogorov-Smirnov test. 
When an exact $p$-value is required for
smaller sample sizes, the methodology in \citet{Conover1972} is used in
for one-sided tests.  For two-sided tests, the methods presented in
\citet{gleser85} lead to exact two-sided $p$-values.  This requires the
calculation of rectangular probabilities for uniform order statistics
as discussed by \citet{nieder81}.
Full details of the calculations are contained in source code
of our revised function \code{ks.test()} and in the papers of
Conover and Gleser.

@@

A different toy example shows the dangers of using R's existing
\code{ks.test()} function:
\begin{Schunk}
\begin{Sinput}
> ks.test(rep(1, 3), ecdf(1:3))
\end{Sinput}
\begin{Soutput}
	One-sample Kolmogorov-Smirnov test

>>>>

This paper presents a revision of R's
\code{ks.test()} function and a new \code{cvm.test()} function to
fill this void for researchers and practitioners in the R environment. This
work was motivated by the need for such goodness-of-fit testing in a study
of Olympic figure skating scoring \citep{emersonarnold2010}.  
We first present overviews of the theory and general implementation of the
discrete Kolmogorov-Smirnov and Cram\'{e}r-von Mises tests.  We discuss
the particular implementation of the tests in R and provide examples.  We
conclude with a short discussion, including the state of existing continuous
and two-sample Cram\'{e}r-von Mises testing in R.

@@

Having obtained the test statistic, the $p$-value must then be calculated. 
For larger sample sizes, the null distribution
of the test statistic can be approximated
with the null distribution from the classical Kolmogorov-Smirnov test. 
When an exact $p$-value is required for
smaller sample sizes, the methodology in \citet{Conover1972} is used in
for one-sided tests.  For two-sided tests, the methods presented in
\citet{gleser85} lead to exact two-sided $p$-values.  This requires the
calculation of rectangular probabilities for uniform order statistics
as discussed by \citet{nieder81}.
Full details of the calculations are contained in source code
of our revised function \code{ks.test()} and in the papers of
Conover and Gleser.

@@

A different toy example shows the dangers of using R's existing
\code{ks.test()} function with discrete data:
\begin{Schunk}
\begin{Sinput}
> ks.test(rep(1, 3), ecdf(1:3))
\end{Sinput}
\begin{Soutput}
	One-sample Kolmogorov-Smirnov test
